CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-10-01 codecheck-paper.tex
add link for Octopus and Hypergraph

As a prerequisite, we see a CODECHECK as part of a typical scholarly
communication process. While more extreme ideas to change the paradigms
how researchers share their work exist [REF Octopus], there is a 
value in an evolutionary approach. Thereby, existing communities can 
transition towards more open practices at their own pace and ensure
no one is left behind unfairly.
When integrating a CODECHECK in existing review and publication processes,
the \emph{turnaround time} is crucial. Depending on when and who conducts
the check, it may be done faster, or add considerably to the overall
time from submission to publication.
% TODO write about our experiences how long a CODECHECK takes?

>>>>

As a prerequisite, we see a CODECHECK as part of a typical scholarly
communication process. While more radical ideas to change the paradigms
how researchers share their work exist\foonote{For example Octopus, 
\url{https://science-octopus.org/about}, or Hypergraph
\url{https://www.libscie.org/hypergraph}.}, there is a 
value in an evolutionary approach. Thereby, existing communities can 
transition towards more open practices at their own pace and ensure
no one is left behind unfairly.
When integrating a CODECHECK in existing review and publication processes,
the \emph{turnaround time} is crucial. Depending on when and who conducts
the check, it may be done faster, or add considerably to the overall
time from submission to publication.
% TODO write about our experiences how long a CODECHECK takes?
